### 2017-01-08 paper/codes/discovery.tex
Pass on text

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    showstringspaces=false
}
\begin{lstlisting}[language=Bash]
for subj in $SUBJECTS; do
    subject_path="$SUBJECTS_HOME/$subj"
    build_files=`find $subject_path -name pom.xml`
    for build_file in $build_files; do
        output=`cat $build_file | grep "parallel\|forkMode\|forkCount"`
        if [ -z $output ]; then echo $build_file; fi
done
\end{lstlisting}
    \caption{\label{fig:discovery-step} Bash script to filter
    build files (\ie, \emph{pom.xml}) with potentially parallelization
    settings. We first find all build files from a subject (line 3).
    Then, we iterate over each path (line 4), list the file content
    (\CodeIn{cat} command), and redirect the output to filter only the
    lines that contain any of the keywords \CodeIn{parallel},
    \CodeIn{forkMode}, or \CodeIn{forkCount} (\CodeIn{grep} command).
    If the output is not empty (line 7), we print the path from the
    current \emph{pom.xml} file to inspect it later.}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    showstringspaces=false
}
\begin{lstlisting}[language=Bash]
for subj in $SUBJECTS; do
    subject_path="$SUBJECTS_HOME/$subj"
    build_files=`find $subject_path -name pom.xml`
    for build_file in $build_files; do
        output=`cat $build_file | grep "parallel\|forkMode\|forkCount"`
        if [ -z $output ]; then echo $build_file; fi
done
\end{lstlisting}
    \caption{\label{fig:discovery-step} Bash script to filter build
    files for inspeciton: line 3 lists all \emph{pom.xml} files from a
    subject; for each path, the  \CodeIn{cat} command lists the file
    content and uses \CodeIn{grep} to filter only the matching lines
    with the keywords \CodeIn{parallel}, \CodeIn{forkMode}, or
    \CodeIn{forkCount} (lines 5-6); if the output is not empty (line
    7), we print the current path.}
\end{figure}

### 2017-01-08 paper/evaluation.tex
Pass on text

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost from a test suite is distributed
among the test cases?}
\newcommand{\RQC}{How often parallelization features appear in
build files?}
\newcommand{\RQD}{What is the impact of parallelization?}
\newcommand{\RQE}{What factors contribute to improve performance
through parallelization?\Jbc{Previously as "When does parallelization
works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of parallelization?}

@@

A Maven project may contain several submodules with multiple
\emph{pom.xml} files. We considered only projects with a
\emph{pom.xml} file located in the root directory.  As of December
30th 2016, our search criteria returned 615 subjects. From the 615
downloaded projects, 46 were not Maven projects and 159 were in a
unstable revision. From these 159 unstable subjects, \Jbc{elaborate
what is unstable (eg, (1) how many could not resolve dependencies? (2)
how many could not compile sources and tests? (3) could not run tests
due to incompatible testing environment?}. Our final set consists in
\numSubjs{} testable subjects.

@@

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS
Trusty Tahr} (64-bit version). Software settings include \Comment{the
Linux \emph{sysstat} package to measure performance, }\emph{git} to
fetch subjects, \emph{Java 8} and \emph{Maven 3.3.9} to build and test
subjects. Our evaluation scripts depends on \emph{Python 3.4} and
\emph{Bash} to execute.  For replication, all source artifacts are
publicly available at \Fix{create gh-pages}, including supporting
scripts (\eg, the script that test subjects and generates the raw
data), and the full list of projects. \Comment{, and a
\emph{Vagrantfile} to emulate our hardware and all software
dependencies.}

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 5-11) iterates over the
list of subjects and invokes Maven in separated steps (lines 7-9). To
avoid inflating the measured time we executed Maven in different
steps: we first compiled the source and test files (line 7), made all
dependencies available locally (line 8) and later, we ran the tests in
offline mode (line 9) to bypass package updates. After the execution,
we used a regular expression on the output log to extract the elapsed
time (line 10). Before collecting the time cost, we executed all
subjects and randomly selected 100 logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static analysis)
to ignore during the experiment (lines 1-3).  To avoid noise from
operating system events, we used a dedicated server remotely via SSH
with the operating system running only essential services (\eg, the
SSH server). In addition, we configured the \CodeIn{isolcpus} option
from the Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs
to execute our experiment and the remaining CPUs to run the operating
system. By isolating a set of virtual CPUs, we prevent
context-switching from the experiment processes and OS-related
process.

@@

\Jbc{Ensure to describe that: subjects that could not run the tests
due to incompatible testing environment were removed (likely to happen
for subjects that rely on database systems and other external
factors), the exit status for all executions are consistent and I
removed flaky projs}

We ran each subject's tests three times and grouped them according to
the time cost (in average): tests that run in less than a minute
(\emph{short} group), tests than run in one minute and less than five
minutes (\emph{medium} group), and tests that run in five (or more)
minutes (\emph{long} group). We based our classification from a
previous work \cite{gligoric-etal-issta2015} and added the
\emph{medium} group due to the variability of the time cost from
subjects out of the \emph{short} group. Figure~\ref{fig:rq1-boxplot}
shows the time cost distribution of each group: the \emph{short} group
is the most right skewed distribution with outliers closed to the
\emph{medium} group and 50\% of the subjects run in less than 15
seconds; the median from the \emph{medium} group is nearly two minutes
and most of the subjects run in less than four minutes; most of the
\emph{long} group runs in less than 25 minutes but has outliers that
require more than 50 minutes to execute. Figure~\ref{fig:rq1-barplot}
summarizes the proportion of subjects from each group.

@@

Given that 19.3\% of the projects (\ie, 82 projects) are costly,
we concluded that time-consuming regression test suites are relatively
frequent in open-source projects.  It is important to mention that
Figure~\ref{fig:rq1-barplot} represents a lower bound for time cost:
some tests may finish early due to a failure since a subject may be
tested in a potentially unstable revision. From the \numSubjs{}
projects, 286 passed all tests and 118 had failures.

@@

We analyzed the distribution of time execution to investigate if most
of the cost is dominated by a small subset of test cases or if the
cost is nearly equally distributed. \Jbc{I shouldn't introduce
parallelization arguments here... May I just proceed to the
methodology?} \Fix{Regression tests that are well distributed may
benefit from parallelism since more tests executes at the same time
while the opposite scenario may require a different approach. In the
later scenario, executing tests in parallel may have insignificant
impact since a small subset of test cases dominates the execution.}

To evaluate how uniformly distribution the execution cost is among
test cases, we \Fix{...elaborate methodology...}

Results indicated that \Fix{...elaborate...}. \Jbc{We may identify
different groups of subjects (\eg, test suites that are more equally
distributed than others) I think the results from this RQ should be
towards this direction}

@@

To evaluate the presence of parallelization settings, we considered
the \numSubjsRqTwo{} subjects from the groups \emph{long} and
\emph{medium} identified in Section~\ref{sec:rqA}. We focused on
these two groups because given that costly test suites exist, we
wanted to analyze if their maintainers are aware of parallelization
settings and how they use these settings.  We computed the
frequency of the parallelism modes (see Section \ref{sec:modes}) using
a semi-automatic approach: we first discover automatically the
relevant build files (\ie, \emph{pom.xml} files) and then we manually
inspect them to eliminate false-positives (\eg, commented
configuration).  Figure~\ref{fig:discovery-step} describes the
discovery step: first, we list the paths of all build file and then we
filter only the build files that contain any of the keywords,
\CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}. Notice
that, for Maven projects, any of these keywords exist in any possible
parallelism configuration \Fix{cite surefire doc}.

@@

From the \numSubjsRqTwo{} subjects, the discovery step checked \Fix{X}
files and yielded \Fix{Y} files to inspect (distributed in \Fix{A}
subjects). \Jbc{How many were valid configurations? Show a contingency
table summarizing results for Medium/Long when we have the results}
\Jbc{Show a histogram with the distribution of parallel modes}.

>>>>

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost from a regression-test is distributed
among the test cases?}
\newcommand{\RQC}{How often parallelization features appear in
build files?}
\newcommand{\RQD}{What is the impact of parallelization?}
\newcommand{\RQE}{What factors contribute to improve performance
through parallelization?\Jbc{Previously as "When does parallelization
works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of parallelization?}

@@

A Maven project may contain several submodules with multiple
\emph{pom.xml} files. We considered only projects with a
\emph{pom.xml} file located in the root directory.  As of December
30th 2016, our search criteria returned 615 subjects. From the
\numSubjsTotal{} downloaded projects, 46 were not Maven projects and
159 were in a unstable revision. From these 159 unstable subjects,
\Jbc{elaborate what is unstable (eg, (1) how many could not resolve
dependencies? (2) how many could not compile sources and tests? (3)
could not run tests due to incompatible testing environment?}. Our
final set consists in \numSubjs{} testable subjects.

@@

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version). Software settings include \Comment{the Linux
\emph{sysstat} package to measure performance, }git to fetch subjects,
Java 8 and Maven 3.3.9 to build and test subjects. Our evaluation
scripts depends on Python 3.4 and Bash to execute and R to analyze the
data. For replication, all source artifacts are publicly available at
\Fix{create gh-pages}, including supporting scripts (\eg, the script
that test subjects and generates the raw data), and the full list of
projects. \Comment{, and a \emph{Vagrantfile} to emulate our hardware
and all software dependencies.}

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 5-11) iterates over the
list of subjects and invokes Maven in separated steps (lines 7-9). To
avoid inflating the measured time we executed Maven in different
steps: we first compiled the source and test files (line 7), made all
dependencies available locally (line 8) and later, we ran the tests in
offline mode (line 9) to bypass package updates. After the execution,
we used a regular expression on the output log to extract the elapsed
time (line 10). Before collecting the time cost, we executed all
subjects and randomly selected 100 logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static analysis)
to ignore during the experiment (lines 1-3).  To avoid noise from
operating system events, we used a dedicated server remotely via SSH
with the operating system running only essential services (\eg, the
SSH server). In addition, we configured the \CodeIn{isolcpus} option
from the Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs
to execute our experiment and the remaining CPUs to run the operating
system. By isolating a set of virtual CPUs, we prevent
context-switching from experiment processes and OS-related processes.

@@

\Comment{\Jbc{Ensure to describe that: subjects that could not run the tests
due to incompatible testing environment were removed (likely to happen
for subjects that rely on database systems and other external
factors), the exit status for all executions are consistent and I
removed flaky projs}}

We ran each subject's tests three times and grouped them according to
the time cost (in average): tests that run in less than a minute
(\shortg{} group), tests than run in one minute and less than five
minutes (\medg{} group), and tests that run in five (or more) minutes
(\longg{} group). We based our classification from a previous work
\cite{gligoric-etal-issta2015} and added the \medg{} group due to the
variability of the time cost from subjects out of the \shortg{} group.
Figure~\ref{fig:rq1-boxplot} shows the time cost distribution of each
group: the \shortg{} group is the most right skewed distribution with
outliers closed to the \medg{} group and 50\% of the subjects run in
less than 15 seconds; the median from the \medg{} group is nearly two
minutes and most of the subjects run in less than four minutes; most
of the \longg{} group runs in less than 25 minutes but has outliers
that require more than 50 minutes to execute.
Figure~\ref{fig:rq1-barplot} summarizes the proportion of subjects
from each group.

@@

Given that \percentMedLongRunning{} of the projects are costly (\ie,
\numMedLong{} projects from \medg{} and \longg{}), we concluded that
time-consuming regression test suites are relatively frequent in
open-source projects.  It is important to mention that
Figure~\ref{fig:rq1-barplot} represents a lower bound for time cost:
some tests may finish early due to a failure since a subject may be
tested in a potentially unstable revision. From the \numSubjs{}
projects, 286 passed all tests and 118 had failures. \Jbc{elaborate
failed subjects: how much \% of the tests failed?}

@@

To evaluate the distribution of time cost, we analyzed the execution
time of each test case from the \numMedLong{} subjects from the
\longg{} and \medg{} groups identified in Section~\ref{sec:rqA}. We
are interested to know whether most of the execution cost of a subject
is dominated by a small subset of test cases or if the cost is nearly
equally distributed. For each subject we calculated the relative
standard deviation of the test cases: we collected the elapsed time of
each individual test, calculated the standard deviation, and divided
by the mean. \Jbc{I need to clarify the relationship
"well/bad-balanced" regression test and relative standard deviation}

Results indicated that \Fix{...elaborate...}. \Jbc{We may identify
different groups of subjects}

\Jbc{I shouldn't introduce parallelization arguments here but we have
to address this at some point:
Regression tests that are well distributed may benefit from
parallelism since more tests executes at the same time while the
opposite scenario may require a different approach. In the later
scenario, executing tests in parallel may have insignificant impact
since a small subset of test cases dominates the execution.}

@@

To evaluate the presence of parallelization settings, we considered
the \numMedLong{} subjects from the \longg{} and \medg{} groups
identified in Section~\ref{sec:rqA}. We focused on these two groups
because given that costly test suites exist, we wanted to analyze if
their maintainers are aware of parallelization settings and how they
use these settings.  We computed the frequency of the parallelism
modes (see Section \ref{sec:modes}) using a semi-automatic approach:
we first discover automatically the relevant build files (\ie,
\emph{pom.xml} files) and then we manually inspect the files to
eliminate false-positives (\eg, a false-positive may occur if the file
contains a commented configuration).  Figure~\ref{fig:discovery-step}
describes the discovery step: first, we list the paths of all build
file and then we filter only the build files that contain any of the
keywords, \CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}.
Notice that, for Maven projects, any of these keywords exist in any
possible parallelism configuration \Fix{cite surefire doc}.

@@

From the \numMedLong{} subjects, the discovery step checked \Fix{X}
files and yielded \Fix{Y} files to inspect (distributed in \Fix{A}
subjects). \Jbc{How many were valid configurations? Show a contingency
table summarizing results for Medium/Long when we have the results}
\Jbc{Show a histogram with the distribution of parallel modes}.
